---
title: "Bioinfoclass7"
author: "gc"
date: "4/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#functions again
we can source any file of R code with the "source" () function
```{r}
source("http://tinyurl.com/rescale-R")
```

lets make sure things are there
```{r}
ls()
```

Check our "rescale() function is working
```{r}
rescale(1:10)
```
```{r, eval=FALSE}
rescale( c(1:10, "string") )
```
Lets check if rescale2 does any better
```{r, eval=FALSE}
rescale2( c(1:10, "string") )
```
##create a new (function step by step). Function for finding missing values in two datasets
How to start?
write a "both_na()" function to do this
# Lets define an example x and y
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)

```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
is.na(x)

```

```{r}
which( is.na(x) )
```

```{r}
which( !is.na(x) )
```
```{r}
sum(is.na(x) )
```

```{r}
is.na(x)
is.na(y)
```
```{r}
is.na(x) & is.na(y)
```

#How many TRUE? are in this vector
```{r}
sum( is.na(x) & is.na(y) )
```
My first fn can start from this snippet
```{r}
both_na <- function(x, y) { sum( is.na(x) & is.na(y) )}
```
Test it
```{r}
both_na( x, y )
```
Testing
```{r}
x <- c(NA, NA, NA)
y1 <- c( 1, NA, NA)
y2 <- c( 1, NA, NA, NA)

both_na( x, y2 )
```
```{r}
both_na2(x, y2)
```
#Refine and polish
make our function more useful by returnig more information

```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
both_na3(x, y)

```
```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
ans <- both_na3(x, y)

```
```{r}
ans$which
```
## One last example
Finding the intersection of two datasets
```{r}
x <- df1$IDs
y <- df2$IDs

x
y
```

# Search for existing functionality to get us started...
??intersect 

```{r}
intersect(x, y)
```
 We can try the intersect() fn and the  %in%  fn
```{r}
intersect(x, y)
```
 
```{r}
x %in% y
```

Now we can try the cbind fn to combine two inputos (i.e vectors) from the same lenght
we can use the logical output in %in% to get at our matching data
```{r}
x[x %in% y]
y[y %in% x]
```
Lets put these togheter as columns of a matrix
```{r}
cbind(x[x %in% y], y[y %in% x])
```
Now we can make our first function for this

```{r}
gene_intersect <- function(x, y) {
 cbind( x[ x %in% y ], y[ y %in% x ] )
}
x <- df1$IDs
y <- df2$IDs

gene_intersect
  
```
Lets try w/datasets
```{r}
gene_intersect2(df1, df2)
```
# Our input $IDs column name may change so lets add flexibility
# By allowing user to specify the gene containing column name
# Experiment first to make sure things are as we expect

```{r}
gene_intersect3(df1, df2)
```
# Next step: Add df1[,gene.colname] etc to our current function

```{r}
gene_intersect4(df1, df2)

```
```{r}
gene_intersect4(df1, df3)

```
lets use the merge fn for this

```{r}
merge(df1, df2, by="IDs")
```









