---
title: "map_colors_function"
author: "gc"
date: "4/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Let look at the poor old function
This is the function code from Barry`s student.
```{r}
# old function
map.colors <- function (value,high.low, palette) {
  proportion <- ((value-high.low[1])/(high.low[2]-high.low[1]))
  index <- round ((length(palette)-1)*proportion)+1
  return (palette[index])
}
```

# Now try to understand this fucntion
```{r}
map.colors2 <- function (x, high.low=range(x), palette=cm.colors(100)) {
  
  #Determine where in the "high.low" range our values of "x" lie"
  precent <- ((x - high.low[1])/(high.low[2] - high.low[1]))
  
  # where in the "palette"" vector of colors is this "precent"
  index <- round ((length(palette)-1) * precent)+1
  
  
  return (palette[index])
}
```
# My first function

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```
# test our first function
```{r}
add(x=6, y=4)
```

```{r}
add(c(1:5), 20)
```
# does this work?
```{r}
add(1, 2, 2)
```
# write my second function

```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

# test my second function
```{r}
rescale(1:10)
```
```{r}
rescale(c(1, 2, NA, 3, 10))
```

```{r}
rescale2 <- function(x) {
 rng <-range(x, na.rm = TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```
```{r}
rescale2(c(1, 2, NA, 3, 10))
```


```{r}
# rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
```
```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
}
```
rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
}
```{r}
rescale3(c(1, 2, NA, 3, 10), plot = TRUE)
```
```{r}
rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=TRUE)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 return(answer)
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
}
```

```{r}
library(bio3d)
```
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")

```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug

```
```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
```

```{r}
library(bio3d)
```

```{r}
s1 <- read.pdb("4AKE") # kinase with drug
```

```{r}
library(bio3d)
```
```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s1
```
```{r}
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.chainA
```
```{r}
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s2.chainA
```

```{r}
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
```
```{r}
s2 <- read.pdb("1AKE") # kinase no drug
s2
```
# my_actual_first_function
```{r}
add <- function(x, y=1)
```

